Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-08-28 text/paper/paper1.tex
refs etc.

Finally, the above-mentioned studies did not control for possible
conflating effects of ``silent prosody''. A growing number of evidence
suggests that numerous factors might influence accent placement and
prosodic phrasing even while reading, amongst them default
accentuation, constituent length, rhythmic phenomena, and individual
variation (Augurzky, 2008; Bader, 1998; Fodor98, 2000, 2001; Kentner,
2012, Steinhauer et.  al., 2001, see also the discussion in Frazier,
2009).\dn{references} As it has been suggested in the theoretical
literature that the availability of a local reading might hinge on the
realization of contrastive stress on the scalar item,
%Even traditionalism maintains that local
%readings are attested, but requiring a contrastive stress on the
%scalar item
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}, it is necessary to
control for potential variation due to potential differences in silent accent placement.
We therefore presented sentences auditorily and addressed the frequently proposed claim 
that local readings are triggered by contrastive
stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
  others?}

>>>>

Finally, the above-mentioned studies did not control for possible
conflating effects of ``silent prosody''. A growing number of evidence
suggests that numerous factors might influence accent placement and
prosodic phrasing even while reading, amongst them default
accentuation, constituent length, rhythmic phenomena, and individual
variation \citep[e.g.][]{Augurzky08,Bader98,Fodor98,Fodor02,Kentner12,
Steinhauer01}. As it has been suggested in the theoretical
literature that the availability of a local reading might hinge on the
realization of contrastive stress on the scalar item,
%Even traditionalism maintains that local
%readings are attested, but requiring a contrastive stress on the
%scalar item
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}, it is necessary to
control for potential variation due to potential differences in silent accent placement.
We therefore presented sentences auditorily and addressed the frequently proposed claim 
that local readings are triggered by contrastive
stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
  others?}
